---
title: "Live Session Unit 4 Assignment"
section: "Section: MSDS 6306 Doing Data Science - 404"
author: "Chaoshun Hu"
date: "June 5, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 1
a. Install the FiveThirtyEight Library
```{r}
#install.packages("fivethirtyeight") if not installed
library(fivethirtyeight)
```
b. In the listing of Dataset in package, assign the eighteenth dataset to an object 'df'
```{r}
df<-college_grad_students
```
c. To see a more detailed list of all data sets, see the package vignette:
```{r}
vignette("fivethirtyeight", package = "fivethirtyeight")
```
d. Using R commands, give the dimensions and column names of this data frame
```{r}
dim(df)
names(df)
```
## Question 2

a.	Write an R command that gives you the column names of the data frame.  Right after that, write one that counts the
 number of columns but not rows.  
 
```{r}
colnames(df)
length(colnames(df))
```

b .Generate a count of each unique major_category in the data frame.  
```{r}
MajorCategory<-unique(df$major_category)
MajorCatNum<-length(MajorCategory)

Counts <- c(1:MajorCatNum)
for (i in 1:MajorCatNum) 
{ Counts[i] <- length(which(df$major_category == MajorCategory[i]))}
major_count <- data.frame(MajorCategory,Counts)
major_count

```

c.	To make things easier to read, put par(las=2) before your plot to make the text perpendicular to the axis.  Make a barplot of major_count.  
```{r}
par(las=2)
barplot(Counts,horiz=TRUE,col=rainbow(11),cex.axis=0.8,cex.lab=1,main="Major category vs Frequency",xlab="Frequency",ylab="Major category",xlim=c(0,30))
```
d.	Write the fivethirtyeight data to a csv file.  
```{r}
write.csv(df,"fivethirtyeight_18.csv",row.names=FALSE)
```

## Question 3 Codebook

Github link is https://github.com/chaoshunh/SMU_MSDS.git
