---
title: "Live Session Unit 5 Assignment"
section: "Section: MSDS 6306 Doing Data Science - 404"
author: "Chaoshun Hu"
date: "June 13, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##1 Data Munging
a.import the .txt file into R so you can process it.  
```{r}
df<-read.table("yob2016.txt",header=FALSE,sep=";")
names(df) <- c("Name", "Gender", "Amount of Children")
```

b.Display the summary and structure of df
```{r}
summary(df)
str(df)
```

c. Find 3 y's at the end of name and display it
```{r}
grep(".yyy$",df[,1],value=TRUE)
```

d. upon finding and remove the misspelled name and save data to object y2016
```{r}
y2016 <- df[-which(df[,1]==grep(".yyy$", df[,1], value=TRUE)),]
```

## 2 Data Merging
a. Like 1a, please import the yob2015.txt file into R
```{r}
y2015<-read.table("yob2015.txt",header=FALSE, sep=",")
names(y2015) <- c("Name", "Gender", "Amount of Children")
```

b. Display the last ten rows in the dataframe
```{r}
tail(y2015,n=10)
```

c.Merge y2016 and y2015 by your Name column; assign it to final.
```{r}
final<-merge(y2015,y2016,by=c("Name","Gender"),na.rm=T)
```

## 3 Data Summary
a. Create a new column called “Total” in final that adds the amount of children in 2015 and 2016 together. 
```{r}
Total<-final[,3]+final[,4]
final$Total<-Total
sum(Total)
```
b.	Sort the data by Total.  What are the top 10 most popular names?
```{r}
final<-final[order(Total, decreasing=TRUE), ] 
```
Show top 10 most popular names
```{r}
final$Name[1:10]
```

c.The client is expecting a girl!  Omit boys and give the top 10 most popular girl’s names.
```{r}
final<-subset(final,final$Gender=="F")
```

d. Write these top 10 girl names and their Totals to a CSV file. Leave out the other columns entirely.
```{r}
Top10GirlNames <- data.frame(Name=final$Name[1:10],Total=final$Total[1:10])
write.csv(Top10GirlNames, file = "Top10GilrNames.csv", row.names = FALSE)
```